Analysis of Odd one out experiment

### 2019-06-03 reports/odd_one_out/analysis_oddoneout.Rmd
increase text size

p <- df_onecat_distances %>% 
  ggplot(aes(x = distance)) + 
  geom_histogram(bins = 30) + 
  theme(aspect.ratio = 1) +
  geom_segment(data = df_segments, aes(x=x,xend=xend,y=y,yend=yend)) +
  annotate(x = qs[3:5]-c(3,1,0), y = c(19,19,19), label = c("2.","3.","4."), geom = "label") +
  ggtitle(sprintf("Kategorie: %s",this_cat)) +
  xlab("Vzdálenost") +
  ylab("Počet")
p  
ggsave(file.path(plots_dir, "Fig_distance_histogram.eps"), p, width = 6, height = 6)  
```

>>>>

p <- df_onecat_distances %>% 
  ggplot(aes(x = distance)) + 
  geom_histogram(bins = 30) + 
  theme(aspect.ratio = 1) +
  geom_segment(data = df_segments, aes(x=x,xend=xend,y=y,yend=yend)) +
  annotate(x = qs[3:5]-c(3,1,-0.6), y = c(19,19,19), label = c("2.","3.","4."), geom = "label", size = 5) +
  ggtitle(sprintf("Kategorie: %s",this_cat)) +
  xlab("Vzdálenost") +
  ylab("Počet")
p  
ggsave(file.path(plots_dir, "Fig_distance_histogram.eps"), p, width = 6, height = 6)  
```
